PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-04-14 refereeResponse.txt

418: I would specifically state that for the large alpha cases runaway growth only occurs at the start, to avoid initial confusion that the slope turns around when the planetesimal supply is depleted.
435: Is this true? I was under the impression that the residual planetesimal population remains? I think this does not seem consistent with the rest of the work...?
	TODO: Change the wording here. Maybe this isnt true. Would the growth mode simply 'flatten' out here?
446: What exactly does alpha being non-negligible mean? Given that alpha is always less than unity, what alpha value marks the transition of the oligarchic growth regime vs, consumption regime? See major comment.
	This is a good point, and I'm not sure if we have a definitive answer. Inspecting figure 11, theh transition seems to occur near alpha ~ 0.1. I think the best thing to do here is to state the converse: for alpha << 1, most encounters result in scattering and you get oligarchic growth. The key finding from this section is that oligarchic growth does not occur when alpha is not << 1. The text has been updated to reflect this.

5. Full disk Simulation
5.1 Initial Conditions
470: Reference of TRAPPIST-1
	Added reference to Gillon 2016 + 2017, Agol 2021
483 I recommend writing Eq. (6) along the lines of 10 g/cm^2 \times A (M_*/M_\odot)(r/1AU)^(-delta) for readability. The Sigma_MMSN is never used so it's not necessary.
	Done
Table 1.
I don't think the notes are necessary
	Content from the notes has been added to the column headers in the table.
I would probably put the planetesimal masses in units of Ceres
	As discussed above, we feel that Ceres masses are too asteroid-belt specific. Instead, we have chosen to display the planetesimal masses in M_earth.
I think Table 1 and Table 2 could be combined
	Table 1 has been merged into table 2.

### 2023-04-14 main.tex
Modify table 1

\begin{table*}
\caption{Summary of Full Disk Simulations}
\begin{tabular}{llllllllll} \hline \hline
Name     & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\delta^{d}$ & $M_{PP}^a$ & $T_{int}^b$ & $T_{int 1}^c$ &  \\ \hline
fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &  1.00                                                         & 456                              & 16,377  &  \\
fdHiShallow    & $5 \times 10^{22}$ & 903,687 & 100                                                        & 0.5                              &  1.19                                                        & 456                              & 16,377  &  \\
fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &  1.08                                                         & 456                              & 16,377 &  \\
fdLo                & $5 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &  1.77 $\times 10^{-3}$                                  & 3,713                              & 133,651 &  \\ \hline
\end{tabular}
\label{tab:sim_properties}
\begin{flushleft}
\textsc{Note} \\ {$^a$ Maximum protoplanet mass [$M_{earth}$] \\
		       $^b$ Integration time [yr] \\
		       $^c$ Rescaled integration time [yr]} \\
\end{flushleft}
\end{table*}

>>>>

% tablesgenerator.com
\begin{table*}
\caption{Summary of Full Disk Simulations}
\begin{tabular}{lccccccc} \hline \hline
Simulation Name & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Initial Planetesimal \\ Mass ($M_{\odot}$)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Initial Planetesimal \\ Count\end{tabular}} & A   & d   & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Maximum Protoplanet\\ Mass ($M_{\odot}$)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Integration Time\\ (yr)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Rescaled Integration\\ Time (yr)\end{tabular}} \\
\hline
fdHi            & $8.37 \times 10^{-6}$                                                                                & 903,687                                                                                   & 100 & 1.5 & 1.0                                                                                              & 456                                                                                 & 16,377                                                                                       \\
fdHiSteep       & $8.37 \times 10^{-6}$                                                                                & 903,687                                                                                   & 100 & 2.5 & 1.19                                                                                             & 456                                                                                 & 16,377                                                                                       \\
fdHiShallow     & $8.37 \times 10^{-6}$                                                                                & 903,687                                                                                   & 100 & 0.5 & 1.08                                                                                             & 456                                                                                 & 16,377                                                                                       \\
fdLo            & $8.37 \times 10^{-6}$                                                                                & 45,185                                                                                    & 1   & 1.5 & $1.77 \times 10^{-3}$                                                                              & 3,713                                                                               & 133,651                                  \\ \hline                                                   
\end{tabular}
\label{tab:sim_properties}
\end{table*}
